---
title: "HW4-test-All the Neural Network Models"
author: "Yuan Yi Chen (Eve)"
date: "2017年6月4日"
output: html_document
---
#**Agenda**

```{r, include = F}
setwd("C:/Users/Eve/Dropbox/UCLA Files/Courses/418 Tools of Data Science/STATS 418 - HW4")
```
#**Agenda**

###**A. Introduction**
###**B. Brief Summarization**
###**C. Take a Look of Our Data**
###**D. Statistical Models**
###**E. Models, AUC and ROC**
  + #####All Features Included
  + #####Limited Features Included

###**F. Conclusion**

  

***

###**A. Introduction**

####This data is provided a Portuguese banking institution which conducted a marketing campaigns to promote their product. Our goal is to predict if the client will subscribe a term deposit (variable y). We will run several models including neural network, random search (GBM), ensemble, random forest, GBM and logistic regression models. We hope to know:
  * The trade off between training time and accuracy.
  * Will feature selection increases the accuracy?


####The general steps are
  * Manipulate our data set (data wrangling & graphs)
  * Apply different models to the clean data set (with all features)
  * Make prediction and view the accuracy and ROC curve
  * Do feature selection (variable importance)
  * Rebuild models based on limited features
  * Make prediction, AUC and ROC curve (with limited features)

####In order to let readers view the explicit results, I would only include 6 models in this report. That is, regarding to neural network models, only the model with highest AUC will be included in this report. Please refer to the other file __ if you want to view the whole results of totally 26 models.

***

###**B. Brief Summarization** 


#####Here are some pros and cons that I saw from the textbook and Quora
Random Forest Model |          
----|-----------------------------------------------------------
**Pros**|
    | 1. Fast to train our training data
    | 2. High accuracy
    | 3. Automatically Generalized our data within the process
**Cons**| 
    | 1. Inconsistent - because it's classification method
    | 2. Hard to interpret the results
    | 3. Slow to predict our testing data
    | 4. Need high computability, which may be expensive
    
***

###**C. Take a Look of Our Data**

```{r, include = F}
#Remove Objects
rm(list=ls())

#Clear Memory
gc(reset=TRUE)

#diR
setwd("C:/Users/Eve/Dropbox/UCLA Files/Courses/418 Tools of Data Science/STATS 418 - HW4")

#Packages
library(readr)   #Use to read data
library(glmnet)  #Use to apply logistic regression
library(ROCR)    #Use to calcuate AUC
library(h2o)     #Use to run logistic regression and random forest 
library(xgboost) #Use to run random forest model
```

#####We totally have 45211 observations, 15 input variables and 1 output variables (y). The description of features are list as following:

Feature |  Type | Description        
----|-----------|------------------------------------------------
job|Categorical |Type of job, categorical: 'admin.','blue-collar','entrepreneur',etc...
marital| Categorical |Marital status, categorical: 'divorced','married','single','unknown'; note: 'divorced' means divorced or widowed
education| Categorical | "unknown","secondary","primary","tertiary"
balance| Numeric | Average yearly balance, in euros 
age| Numeric | age
housing| Binary |Has housing loan? (binary: "Y","N")
loan| Binary | Has personal loan? (binary: "Y","N")
contact| Categorical | Contact communication type, categorical: "unknown","telephone","cellular"
day| Numeric |Last contact day of the month
month | Categorical |Last contact month of year, categorical: "jan", "feb", "mar", ..., "nov", "dec"
duration |Numeric |Last contact duration, in seconds
campaign |Numeric |Number of contacts performed during this campaign and for this client
pdays |Numeric |Number of days that passed by after the client was last contacted from a previous campaign
previous |Numeric |Number of contacts performed before this campaign and for this client
poutcome|Categorical |Outcome of the previous marketing campaign, categorical: "unknown","other","failure","success"
**y (output)** |Binary |Has the client subscribed a term deposit? (binary: "Y","N")

####**1. Neural Network**
```{r, include = F}
library(h2o)
```
```{r, include = F}
h2o.no_progress()
```

```{r, include = F}
h2o.init(nthreads=-1)
```

```{r}
#Split data sets: train, validation and test
dx <- h2o.importFile("test.csv")
dx_split <- h2o.splitFrame(dx, ratios = c(0.6,0.2), seed = 123)
dx_train <- dx_split[[1]]
dx_valid <- dx_split[[2]]
dx_test <- dx_split[[3]]
Xnames <- setdiff(names(dx_train),"y")
```

```{r}
#Neural Network Model (the Best, highest AUC)
system.time({
  md_nn <- h2o.deeplearning(x = Xnames, y = "y", training_frame = dx_train, validation_frame = dx_valid,
            activation = "Rectifier", hidden = c(50,50), 
            adaptive_rate = FALSE, rate = 0.01, rate_annealing = 1e-04, 
            momentum_start = 0.5, momentum_ramp = 1e5, momentum_stable = 0.99,
            epochs = 100, stopping_rounds = 2, stopping_metric = "AUC", stopping_tolerance = 0) 
})
```
```{r}
#AUC
h2o.performance(md_nn, dx_test)@metrics$AUC
```
